Weighted Model Counting with Conditional Weights

### 2020-07-29 paper/paper.tex
A bit of writing

\title{Weighted Model Counting with Conditional Measures}
\author{Paulius Dilkas}

@@

\begin{itemize}
\item The Main Narrative
  \begin{enumerate}
  \item When weights are defined on literals, the measure on the free BA is
    fully independent.
  \item This means that the BA itself must be larger (i.e., have additional
    `meaningless' literals) to turn any probability distribution into an
    independent one.
  \item We show how we can define conditional weights on literals, allowing us
    to encode any probability distribution into a Boolean algebra that's not
    necessarily independent and thus can be smaller.
  \item We demonstrate a specific example of this by presenting a new way to
    encode Bayesian networks into instances of WMC and adapting a WMC algorithm
    (ADDMC) to run on the new format.
  \item We show that this results in significantly faster inference.
  \item We show that our encoding results in asymptotically fewer literals and
    fewer ADDs, and thus a simpler problem.
  \item (Maybe) we experimentally demonstrate a phase transition based on the
    number of variables per ADD.
  \end{enumerate}
\item Potential criticism may be that this is a step backwards and doesn't allow
  us to use SAT-based techniques for probabilistic inference. However, they can
  still be used for the 'theory+query' part.
  \begin{itemize}
  \item Zero-probability weights and one-probability weights can be interpreted
    as logical clauses. This doesn't affect ADDMC but could be useful for other
    solvers.
  \end{itemize}
\item[F] What are the main claims, what are the main takeaways, intuitive [???]
  of theorems to follow. To do this, we appeal to algebraic constructions to
  define the main concepts for introducing measures on Boolean algebras.
\item
  Algorithms\footnote{\url{http://beyondnp.org/pages/solvers/model-counters-exact/}}
  \begin{itemize}
  \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
    multiplicativity of BAs in different words) (with optimal settings)
  \item Cachet \cite{DBLP:conf/sat/SangBBKP04}
  \item c2d \cite{DBLP:conf/ecai/Darwiche04}
  \item d4 \cite{DBLP:conf/ijcai/LagniezM17} (closed source, boo!)
  \item miniC2D  \cite{DBLP:conf/ijcai/OztokD15}
  \end{itemize}
\item Notable previous/related work
  \begin{itemize}
  \item Hailperin's approach to probability logic
    \cite{DBLP:journals/ndjfl/Hailperin84}
  \item Nilsson's (somewhat successful) probabilistic logic
    \cite{DBLP:journals/ai/Nilsson86,DBLP:journals/ai/Nilsson93}
  \item Logical induction: a big paper with a good overview of previous attempts
    to assign probabilities to logical sentences in a sensible way
    \cite{DBLP:journals/eccc/GarrabrantBCST16}
  \item Measures on Boolean algebras
    \begin{itemize}
    \item On possibility and probability measures in finite Boolean algebras
      \cite{DBLP:journals/soco/CastineiraCT02}
    \item Representation of conditional probability measures
      \cite{krauss1968representation}
    \end{itemize}
  \end{itemize}
\item Intuitively, a measure is just like a probability, except it's in
  $\mathbb{R}_{\ge 0}$ instead of $[0, 1]$.
\item Somewhere: explain things line CNF, CPT, etc.
\end{itemize}

@@

\todo[inline,caption={}]{
  \begin{itemize}
  \item[F] Give a concrete example of something impossible to represent
    using WMC.
  \item[F] Can you say something here about factorized vs non-factorized weight
    function definitions? That is, factorized is when $w$ maps literals to
    $R_{\ge 0}$, non-factorized is when $w$ maps models to $R_{\ge 0}$ and
    \begin{itemize}
    \item come up with nice example when non-factorized weights are intuitive;
    \end{itemize}
  \end{itemize}
}

@@

Let $V$ denote the set of random variables in a Bayesian network. For any random
variable $X \in V$, let $\mathrm{pa}(X)$ denote the set of parents of $X$ and
$\im X$ denote the set of possible values. We will use the Bayesian network in
\cref{fig:example_bn} (loosely based on an example by Sang et al.
\cite{DBLP:conf/aaai/SangBK05}) as a running example throughout this section.
For the Bayesian network in \cref{fig:example_bn}, we have:
\begin{align*}
  V &= \{ W, F, T \}, \\
  \mathrm{pa}(W) &= \emptyset, \\
  \mathrm{pa}(F) &= \mathrm{pa}(T) = \{ W \}, \\
  \im W &= \im F = \{ 0, 1 \}, \\
  \im T &= \{ l, m, h \}.
\end{align*}

\begin{definition}[Indicator variables]
  Let $X \in V$ be a random variable. If $X$ is binary (i.e., $|\im X| = 2$), we
  can arbitrary identify one of the values as $1$ and the other one as $0$ (i.e,
  $\im X \cong \{ 0, 1 \}$). Then $X$ can be represented by a single
  \emph{indicator variable} $\lambda_{X=1}$. For notational simplicity, for any
  set $S$, whenever we write $\lambda_{X=0} \in S$ or $S = \{ \lambda_{X=0},
  \dots \}$, we actually mean $\lambda_{X=1} \not\in S$,

@@

\todo[inline]{Come up with a less repetitive wording.}
For the Bayesian network in \cref{fig:example_bn}, we have:
\begin{align*}
  E(W) &= \{ \lambda_{W=1} \}, \\
  E(F) &= \{ \lambda_{F=1} \}, \\
  E(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h} \}, \\
  E^*(W) &= \{ \lambda_{W=1} \}, \\
  E^*(F) &= \{ \lambda_{F=1}, \lambda_{W=1} \}, \\
  E^*(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h}, \lambda_{W=1} \}.
\end{align*}

@@

\todo[inline]{Ditto.}
For the Bayesian network in \cref{fig:example_bn}, we have:
\begin{align*}
  \mathrm{CPT_W} &= 0.5[\lambda_{W=1}]+0.5\overline{[\lambda_{W=1}]} = 0.5 \cdot 1, \\
  \mathrm{CPT_F} &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4[\lambda_{F=0}] \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}] \\
    &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4\overline{[\lambda_{F=1}]} \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot \overline{[\lambda_{W=1}]} + 0.9\overline{[\lambda_{F=1}]} \cdot \overline{[\lambda_{W=1}]}, \\
  \mathrm{CPT_T} &= ([\lambda_{T=l}] + [\lambda_{T=m}] + [\lambda_{T=h}]) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=m}]}) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=h}]}) \cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot (\dots).
\end{align*}

\todo[inline]{Describe \cref{alg:encoding}}

@@

\subsection{Textual Representation}

The Bayesian network in \cref{fig:example_bn} can be represented in a textual
format as
\[
  \begin{array}{l r r l l}
    \lambda\sb{T=l} &\lambda\sb{T=m} &\lambda\sb{T=h} & &0 \\
                    &-\lambda\sb{T=l} &-\lambda\sb{T=m} & &0 \\
                    &-\lambda\sb{T=l} &-\lambda\sb{T=h} & &0 \\
                    &-\lambda\sb{T=m} &-\lambda\sb{T=h} & &0 \\
    w &\lambda\sb{W=1} & &0.5 &0.5 \\
    w &\lambda\sb{F=1} &\lambda\sb{W=1} &0.6 &0.4 \\
    w &\lambda\sb{F=1} &-\lambda\sb{W=1} &0.1 &0.9 \\
    w &\lambda\sb{T=l} &\lambda\sb{W=1} &0.2 &1 \\
    w &\lambda\sb{T=m} &\lambda\sb{W=1} &0.4 &1 \\
    w &\lambda\sb{T=h} &\lambda\sb{W=1} &0.4 &1 \\
    w &\lambda\sb{T=l} &\lambda\sb{W=0} &0.6 &1 \\
    w &\lambda\sb{T=m} &\lambda\sb{W=0} &0.3 &1 \\
    w &\lambda\sb{T=h} &\lambda\sb{W=0} &0.1 &1
  \end{array}
\]
with each $\lambda$ replaced with a unique positive integer. This format is
based on the format used by the Cachet solver \cite{DBLP:conf/sat/SangBBKP04}
to encode WMC problems, which extends the DIMACS format for CNF formulas with
weight clauses. Subsequently, we extend it in two ways:
\begin{itemize}
\item a single weight clause now supports an arbitrary number of literals,
\item and each weight clause has two probabilities instead of one (i.e., we no
  longer assume that $\Pr(v) + \Pr(\neg v) = 1$ for all variables $v \in U$).
\end{itemize}
The way we use this encoding, it is always the case that either both
probabilities sum to one, or the second probability (i.e., the probability for
the complement of the variable) is equal to one.

@@

\begin{itemize}
\item We don't compare 'compile times' because our encoding time is linear, so
  we would easily beat everyone else.
\item When the Bayesian network has an evidence file, we compute the probability
  of evidence. Otherwise, let $X$ denote the last-mentioned node in the Bayesian
  network. If $\mathsf{true}$ is a valid value of $X$, we compute the marginal
  probability of $X = \mathsf{true}$. Otherwise, we pick the first value of $X$
  and calculate its marginal probability. This applies to the Grid data set (as
  intended) and also to two instances of Plan Reconstruction and roughly half of
  the instances from 2004-PGM that have empty evidence files.
\item The experiments were run on Intel Xeon Gold 6138 processor with an
  \SI{8}{\giga\byte} memory limit.
\item I will call my encoding \texttt{db20}.
\item All other encodings are implemented in
  Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and were compiled
  with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
  \texttt{-noEclause} (i.e., only use standard syntax) flags.
\item We don't use Ace's evidence-encoding mechanism because it has multiple
  significant bugs (and the code is closed-source). Ace's implementation
  (depending on the exact encoding) is supposed to perform some simplifications
  when encoding evidence. We just do the trivial thing---no simplifications.
\item \texttt{cd05} relaxes the encoding so much that extra models become
  possible. They are supposed to be filtered out by the algorithm, but mine
  can't do that because it doesn't deal with models. Same for \texttt{cd06}
  because it's based on \texttt{cd05}.
\item Observations
  \begin{itemize}
  \item The order of the encodings from best to worst is exactly the opposite of
    that in the previous literature.
  \item Our encoding is particularly promising on instances of Grid networks.
    They are set up so that the entire Bayesian network is relevant to the
    query.
  \item However, \texttt{db20} struggles with instances from Mastermind and
    Random Blocks domains (but so does \texttt{sbk05}). We conjecture that this
    is so either because the particular structure of these problems confuse the
    algorithm's heuristics or because these instances allow for significant
    simplifications that are exploited by $\mathtt{d02}$ but not
    $\mathtt{db20}$.
  \end{itemize}
\end{itemize}

\paragraph{Data.} For experiments, we use the Bayesian networks available
with Ace\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and
Cachet\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}, most of
which happen to be binary. We classify them into the following seven categories:
\begin{itemize*}
\item DQMR and
\item Grid networks as described by Sang et al. \cite{DBLP:conf/aaai/SangBK05},
\item Friends and Smokers,
\item Mastermind, and
\item Random Blocks from the work of Chavira et al.
  \cite{DBLP:journals/ijar/ChaviraDJ06},
\item remaining binary Bayesian networks that include Plan Recognition
  \cite{DBLP:conf/aaai/SangBK05}, Students and Professors
  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
\item non-binary classic Bayesian networks (\texttt{alarm}, \texttt{diabetes},
  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
  \texttt{pathfinder}, \texttt{pigs}, \texttt{water}).
\end{itemize*}

>>>>

\title{Weighted Model Counting with Conditional Weights}
\author{Paulius Dilkas}

@@

\begin{itemize}
\item The Main Narrative
  \begin{enumerate}
  \item When weights are defined on literals, the measure on the free BA is
    fully independent.
  \item This means that the BA itself must be larger (i.e., have additional
    `meaningless' literals) to turn any probability distribution into an
    independent one.
  \item We show how we can define conditional weights on literals, allowing us
    to encode any probability distribution into a Boolean algebra that's not
    necessarily independent and thus can be smaller.
  \item We demonstrate a specific example of this by presenting a new way to
    encode Bayesian networks into instances of WMC and adapting a WMC algorithm
    (ADDMC) to run on the new format.
  \item We show that this results in significantly faster inference.
  \item We show that our encoding results in asymptotically fewer literals and
    fewer ADDs, and thus a simpler problem.
  \item (Maybe) we experimentally demonstrate a phase transition based on the
    number of variables per ADD.
  \end{enumerate}
\item Potential criticism may be that this is a step backwards and doesn't allow
  us to use SAT-based techniques for probabilistic inference. However, they can
  still be used for the 'theory+query' part.
  \begin{itemize}
  \item Zero-probability weights and one-probability weights can be interpreted
    as logical clauses. This doesn't affect ADDMC but could be useful for other
    solvers.
  \end{itemize}
\item[F] What are the main claims, what are the main takeaways, intuitive [???]
  of theorems to follow.
\item
  Algorithms
  \begin{itemize}
  \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
    multiplicativity of BAs in different words) (with optimal settings)
  \item Cachet \cite{DBLP:conf/sat/SangBBKP04}
  \item c2d \cite{DBLP:conf/ecai/Darwiche04}
  \item d4 \cite{DBLP:conf/ijcai/LagniezM17} (closed source, boo!)
  \item miniC2D  \cite{DBLP:conf/ijcai/OztokD15}
  \end{itemize}
\item Notable previous/related work
  \begin{itemize}
  \item Hailperin's approach to probability logic
    \cite{DBLP:journals/ndjfl/Hailperin84}
  \item Nilsson's (somewhat successful) probabilistic logic
    \cite{DBLP:journals/ai/Nilsson86,DBLP:journals/ai/Nilsson93}
  \item Measures on Boolean algebras
    \begin{itemize}
    \item On possibility and probability measures in finite Boolean algebras
      \cite{DBLP:journals/soco/CastineiraCT02}
    \item Representation of conditional probability measures
      \cite{krauss1968representation}
    \end{itemize}
  \end{itemize}
\item Intuitively, a measure is just like a probability, except it's in
  $\mathbb{R}_{\ge 0}$ instead of $[0, 1]$.
\end{itemize}

@@

\todo[inline,caption={}]{
  Examples (must):
  \begin{itemize}
  \item an example of a measure that cannot be expressed using a factored weight
    function,
  \item an example of how to express it using conditional weight functions.
  \end{itemize}
  Also, define `conditional weight function'.
}

@@

\todo[inline]{Define 'CPT'}

In line with the names of previous encodings, we shall call this encoding
\texttt{db20}. Let $V$ denote the set of random variables in a Bayesian network.
For any random variable $X \in V$, let $\mathrm{pa}(X)$ denote the set of
parents of $X$ and $\im X$ denote the set of possible values. We will use the
Bayesian network in \cref{fig:example_bn} as a running example throughout this
section. For this network, $V = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$,
$\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and
$\im T = \{ l, m, h \}$.

\begin{definition}[Indicator variables]
  Let $X \in V$ be a random variable. If $X$ is binary (i.e., $|\im X| = 2$), we
  can arbitrary identify one of the values as $1$ and the other one as $0$ (i.e,
  $\im X \cong \{ 0, 1 \}$). Then $X$ can be represented by a single
  \emph{indicator variable} $\lambda_{X=1}$. For notational simplicity, for any
  set $S$, we write $\lambda_{X=0} \in S$ or $S = \{ \lambda_{X=0}, \dots \}$ to
  mean $\lambda_{X=1} \not\in S$,

@@

For the Bayesian network in \cref{fig:example_bn}, this gives us:
\begin{align*}
  E(W) &= \{ \lambda_{W=1} \}, \\
  E(F) &= \{ \lambda_{F=1} \}, \\
  E(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h} \}, \\
  E^*(W) &= \{ \lambda_{W=1} \}, \\
  E^*(F) &= \{ \lambda_{F=1}, \lambda_{W=1} \}, \\
  E^*(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h}, \lambda_{W=1} \}.
\end{align*}

@@

\todo[inline]{Describe the algorithm and the CPT functions.}

For the Bayesian network in \cref{fig:example_bn}, we have:
\begin{align*}
  \mathrm{CPT_W} &= 0.5[\lambda_{W=1}]+0.5\overline{[\lambda_{W=1}]} = 0.5 \cdot 1, \\
  \mathrm{CPT_F} &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4[\lambda_{F=0}] \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}] \\
    &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4\overline{[\lambda_{F=1}]} \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot \overline{[\lambda_{W=1}]} + 0.9\overline{[\lambda_{F=1}]} \cdot \overline{[\lambda_{W=1}]}, \\
  \mathrm{CPT_T} &= ([\lambda_{T=l}] + [\lambda_{T=m}] + [\lambda_{T=h}]) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=m}]}) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=h}]}) \cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot (\dots).
\end{align*}

@@

\subsection{Textual Representation} \label{sec:textual_representation}

\todo[inline]{Describe how this is an intermediate step before we get the $\phi$
from the algorithm. Each CPT is treated as a clause.}

The Bayesian network in \cref{fig:example_bn} can be represented in a textual
format as
\[
  \begin{array}{l r r l l}
    \lambda\sb{T=l} &\lambda\sb{T=m} &\lambda\sb{T=h} & &0 \\
                    &-\lambda\sb{T=l} &-\lambda\sb{T=m} & &0 \\
                    &-\lambda\sb{T=l} &-\lambda\sb{T=h} & &0 \\
                    &-\lambda\sb{T=m} &-\lambda\sb{T=h} & &0 \\
    w &\lambda\sb{W=1} & &0.5 &0.5 \\
    w &\lambda\sb{F=1} &\lambda\sb{W=1} &0.6 &0.4 \\
    w &\lambda\sb{F=1} &-\lambda\sb{W=1} &0.1 &0.9 \\
    w &\lambda\sb{T=l} &\lambda\sb{W=1} &0.2 &1 \\
    w &\lambda\sb{T=m} &\lambda\sb{W=1} &0.4 &1 \\
    w &\lambda\sb{T=h} &\lambda\sb{W=1} &0.4 &1 \\
    w &\lambda\sb{T=l} &\lambda\sb{W=0} &0.6 &1 \\
    w &\lambda\sb{T=m} &\lambda\sb{W=0} &0.3 &1 \\
    w &\lambda\sb{T=h} &\lambda\sb{W=0} &0.1 &1
  \end{array}
\]
with each $\lambda$ replaced with a unique positive integer. This format is
based on the format used by the Cachet solver \cite{DBLP:conf/sat/SangBBKP04}
to encode WMC problems, which extends the DIMACS format for conjunctive normal
form (CNF) formulas with weight clauses. Subsequently, we extend it in two
ways:
\begin{itemize}
\item a single weight clause now supports an arbitrary number of literals,
\item and each weight clause has two probabilities instead of one (i.e., we no
  longer assume that $\Pr(v) + \Pr(\neg v) = 1$ for all variables $v \in U$).
\end{itemize}
The way we use this encoding, it is always the case that either both
probabilities sum to one, or the second probability (i.e., the probability for
the complement of the variable) is equal to one.

@@

\begin{itemize}
\item We chose not to measure or compare encoding time because of different
  languages of implementation and the fact that our encoding algorithm (i.e.,
  the process that converts a Bayesian network into a textual encoding such as
  in \cref{sec:textual_representation}) is linear in the total number of CPT
  rows and so is unlikely to be slower than, e.g., \texttt{cd06}, which relies
  on solving $\NP$-complete problems as part of the encoding process
  \cite{DBLP:conf/sat/ChaviraD06}.
\item Whenever a Bayesian network comes with an evidence file, we compute the
  probability of evidence. Otherwise, let $X$ denote the last-mentioned node in
  the Bayesian network. If $\mathsf{true}$ is a valid value of $X$, we compute
  the marginal probability of $X = \mathsf{true}$. Otherwise, we pick the value
  of $X$ which is listed first and calculate its marginal probability.
\item The experiments were run on Intel Xeon Gold 6138 processor with an
  \SI{8}{\giga\byte} memory limit.
\item For all other encodings, we use their implementation in
  Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} with
  \texttt{-encodeOnly} and \texttt{-noEclause} flags. However, Ace was not used
  to encode evidence, as preliminary experiments revealed that the
  evidence-encoding implementation contains bugs that can lead to incorrect
  answers or a Java exception being thrown on some instances of the data set
  (and the source code is not publicly available). Instead, we simply list all
  the evidence as additional clauses in the encoding (regardless of which
  encoding is used).
\item Note that \texttt{cd05} and \texttt{cd06} purposefully produce overly
  relaxed encodings that contain extra models and thus yield incorrect
  probabilities \cite{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}.
  These additional models are supposed to be filtered out during circuit
  compilation \cite{DBLP:conf/ijcai/ChaviraD05}, but this is not easily
  achievable with ADDMC. Nonetheless, we include both encodings in our timing
  experiments.
\end{itemize}

\paragraph{Data.} For experiments, we use the Bayesian networks available
with Ace and
Cachet\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}, most of
which happen to be binary. We classify them into the following seven categories:
\begin{itemize*}
\item DQMR and
\item Grid networks as described by Sang et al. \cite{DBLP:conf/aaai/SangBK05},
\item Friends and Smokers,
\item Mastermind, and
\item Random Blocks from the work of Chavira et al.
  \cite{DBLP:journals/ijar/ChaviraDJ06},
\item remaining binary Bayesian networks that include Plan Recognition
  \cite{DBLP:conf/aaai/SangBK05}, Students and Professors
  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
\item non-binary classic Bayesian networks (\texttt{alarm}, \texttt{diabetes},
  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
  \texttt{pathfinder}, \texttt{pigs}, \texttt{water}).
\end{itemize*}

\paragraph{Observations.}
\begin{itemize}
\item The order of the encodings from best to worst is exactly the opposite of
  that in the previous literature.
\item Our encoding is particularly promising on instances of Grid networks.
  They are set up so that the entire Bayesian network is relevant to the
  query.
\item However, \texttt{db20} struggles with instances from Mastermind and
  Random Blocks domains (but so does \texttt{sbk05}). We conjecture that this
  is so either because the particular structure of these problems confuse the
  algorithm's heuristics or because these instances allow for significant
  simplifications that are exploited by $\mathtt{d02}$ but not
  $\mathtt{db20}$.
\end{itemize}
